### 2017-06-07 paper.tex
Updating to latest version of PLOS template

Another example is Software Carpentry's instructor training program.
First offered in 2012,
is now a two-day course delivered both in-person and online
\cite{lessons-learned}.
Not only does it teach good pedagogical practices,
it serves and an onboarding process to get everyone on the same page
regarding who lessons are for,
how they are delivered,
and how they are maintained.

@@

A lesson release is a good opportunity to bring the material into a stable shape
by fixing outstanding issues and merging contributions.
Version control helps a lot in continuously maintaining a list of contributors
but also in remembering which version is used for release
(e.g., using branches or tags).
Lesson releases should use a consistent naming scheme,
such as the full year and month of the release,
e.g. ``2017.05''.

@@

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
%

@@

>>>>

Another example is Software Carpentry's instructor training program.
First offered in 2012,
is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
Not only does it teach good pedagogical practices,
it serves and an onboarding process to get everyone on the same page
regarding who lessons are for,
how they are delivered,
and how they are maintained.

@@

A lesson release is a good opportunity to bring the material into a stable shape
by fixing outstanding issues and merging contributions.
Version control helps a lot in continuously maintaining a list of contributors
but also in remembering which version is used for release
(e.g., using branches or tags).
Lesson releases should use a consistent naming scheme,
such as the full year and month of the release,
e.g. ``2017.05''.
This is the scheme Software Carpentry has used in
its releases of its lessons \cite{shell2015,shell2017}.

@@

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for
% step-by-step instructions.

@@

\bibitem{instructor-training}
Christina Koch and Greg Wilson (eds.)
\newblock Software Carpentry: Instructor Training; 2016.
\newblock \url{https://zenodo.org/record/57571#.WS8huDOZPdQ}.

\bibitem{how-to-teach-programming}
Wilson G.
\newblock How to Teach Programming (And Other Things).
\newblock Lulu.com; 2017.

\bibitem{shell2015}
Gabriel A.~Devenyi and Christina Koch (eds.):
Software Carpentry: The Unix Shell; 2015.
\newblock \url{https://zenodo.org/record/27355#.WS8lajOZPdQ}.

\bibitem{shell2017}
Gabriel A.~Devenyi and Ashwin Srinath (eds.):
Software Carpentry: The Unix Shell; 2017.
\newblock \url{https://zenodo.org/record/278226#.WS74tTOZPdQ}.
